Local to Global Mariculture Modelling

### 2025-07-28 index.qmd
Move functional response to index.qmd

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true
  freeze: auto
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
---

@@

This project contains a comprehensive analysis of mariculture modelling from local to global scales. Below you'll find links to all the main documentation pages:

| Page | Description |
|---------|:-------------------------------------------------|
| **[Data Tidying](01_tidying_data.html)** | Initial data cleaning and preparation procedures |
| **[Extracting Production Locations](02_extracting_production_locations.html)** | Identification and processing of mariculture production site locations |
| **[Assessing Species Potential](03_assessing_species_potential.html)** | Evaluation of species suitability for different locations |
| **[Extracting Temperatures](04_extracting_temperatures.html)** | Temperature data extraction and processing for model inputs |
| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition analysis and formulation procedures |
| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model implementation and execution |
| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers |
| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input patterns and their relative impacts |

# Data analysis

```{r setup}
#| include: false
#| eval: true
#| cache: false
#| message: false

library(magrittr)
library(units)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(purrr)
library(future)
library(readxl)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()

@@

# Filenames
# species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
# pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))

@@

>>>>

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true
  freeze: auto
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

@@

All code and processes for this project are linked below. Note that some scripts require access to raw data which is not stored on Github. 
While this page (the index) has code that runs prior to rendering, all code in the subsequent pages has not been run for rendering.

## Main analysis

The main analysis for this project focuses on the differences in total protein, carbohydrate, lipid and nitrogen losses between feeds.

| Page | Description |
|---------|:-------------------------------------------------|
| **[Data Tidying](01_tidying_data.html)** | Initial data tidying and preparation |
| **[Extracting Production Locations](02_extracting_production_locations.html)** | Identification and processing of mariculture production site locations |
| **[Assessing Species Potential](03_assessing_species_potential.html)** | Evaluation of species suitability for different locations |
| **[Extracting Temperatures](04_extracting_temperatures.html)** | SST data extraction and processing for model inputs |
| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition formulation for model runs |
| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model execution |

## Extra analysis

The extra analyses for this project involved some exploration into potential impacts of nutrient losses. This will likely not make it into the final manuscript.

| Page | Description |
|---------|:-------------------------------------------------|
| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers |
| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input patterns and their relative impacts |

```{r setup}
#| cache: false
#| message: false

library(magrittr)
library(units)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(purrr)
library(future)
library(readxl)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect())
# This markdown uses TinyTex - install with tinytex::install_tinytex()

@@

@@

```{r}
#| label: fig-functional-response-to-temperature
#| eval: false
#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.

all_params <- c(
  find_read(output_species_data_path, "species_params"),
  find_read(output_species_data_path, "pop_params")
)

func_T_resp <- data.frame(water_temp = seq(-5, 26, 0.25))
weight <- 1000

# Relative feeding rate with temperature
func_T_resp$feeding_rate <- sapply(
  FUN = feeding_rate, 
  X = func_T_resp$water_temp, 
  species_params = all_params
)

# Maximum potential ingestion (g) at temperature
func_T_resp$ing_pot <- all_params['meanImax'] * (weight^all_params['m']) * func_T_resp$feeding_rate

# Food provided is based on calculated potential ingestion BUT if temperature is too low they are still provided with the food that would be required at lowest temperature (when feeding rate is ~18.3%)
func_T_resp$food_prov <- food_prov_rate(
  water_temp = func_T_resp$water_temp, 
  ing_pot = func_T_resp$ing_pot,
  ing_pot_min = all_params['meanImax'] * (weight^all_params['m']) * feeding_rate(all_params['Taa'], all_params),
  species_params = all_params,
  pop_params = all_params
)

func_T_resp$food_enc <- all_params['eff'] * func_T_resp$food_prov
func_T_resp <- func_T_resp %>% 
  mutate(ing_act = pmin(food_enc, ing_pot))

func_T_resp %>% 
  ggplot(aes(x = water_temp, y = ing_act)) +
  geom_line(linewidth = 0.75) +
  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
  # scale_y_continuous(breaks = seq(0,1.5,0.25)) +
  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
  labs(x = expression("Water temperature ("*degree*"C)"), y = "Feedd ingested/provided") +
  prettyplot()
```

```{r}
#| label: patchwork-map-mercator
#| fig-cap: |
#|   Example of a patchwork
#| fig-height: 9
#| fig-width: 9.5

p_bigmap_feeding <- p_bigmap_mercator +
  geom_sf(data = feeding, aes(color = prop_feed_eaten, geometry = geometry), size = 2) +
  scale_color_viridis_c(option = "turbo") +
  guides(col = guide_colourbar(
    title = "Proportion of provided feed eaten",
    direction = "vertical", position = "right",
    label.position = "right", title.position = "top", 
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
    barwidth = 1.5, barheight = 20
  )) +
  prettyplot() +
  labs(y = "Latitude", x = "Longitude")

patchwork_mercator(p_bigmap_feeding)
```
